Disparity through time figures

### 2017-12-21 analyses/05-figure-dtt.Rmd
Edit to fit Bapst and Brusatte rescaled

brusatte_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

brusatte_s <- 
  brusatte_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 70, y = 0.15, label = "Brusatte2014")

@@

```{r}
bapst_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 75, y = 0.15, label = "Bapst2016")

@@

```{r}
bapst_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 75, y = 0.15, label = "Bapst2016")

>>>>

brusatte_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(170, 70),
                  breaks = c(seq(170, 70, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

brusatte_s <- 
  brusatte_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 140, y = 0.15, label = "Brusatte2014")

@@

```{r}
bapst_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(200, 50),
                  breaks = c(seq(200, 50, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 120, y = 0.15, label = "Bapst2016")

@@

```{r}
bapst_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(200, 50),
                  breaks = c(seq(200, 50, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 165, y = 0.15, label = "Bapst2016")
